---
title: "Happiness Report"
author: "Zhu Shen"
date: "November 6, 2018"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(MASS)
library(reshape2)
library(ggthemes)
library(stargazer)
library(glmpathcr)
library(gridExtra)
```

## R Markdown
```{r, include = FALSE}
wave_6_happiness <- readRDS("F00007762-WV6_Data_R_v20180912.rds", refhook = NULL)
```

## Define Functions 
```{r}
color_list = list('#4E79A7','#F28E2B','#E15759','#76B7B2','#59A14F','#EDC948','#B07AA1','#FF9DA7',
              '#9C755F','#BAB0AC')
stats_plot <- function(income_scale){
  by_income_scale <- questions_variable %>%
  filter(Income_Scale == income_scale) %>%
  group_by(Income_Inequality) %>%
  summarize(count = n()) %>%
  mutate(total = sum(count), 
         prop = count/total)

p <- ggplot(by_income_scale,aes(x=Income_Inequality,y=prop, width=.6))+
  geom_bar(stat="identity", fill = color_list[[income_scale]])+
  scale_x_discrete(name ="Level", 
                   breaks=seq(0,10,1)) + 
  ylab("Proportion") +
  theme_bw()+ 
  labs(title = paste("Attitute of Income Inequality across Income Scales (Income Scale: ",  income_scale, ")"), 
       subtitle = 
         "Level 1: Income should be made more equal\nLevel 10: Larger income differences as incentives",
       caption = "Source: World Value Survey")
p
}

```

## Brief Speculation fo the dataset

```{r}
# Find the keyword TRUST
questions_trust <- c(paste("V", c(24, 102:107), sep = ''))
#confounding_trust <- "V160B" 

# According to Paper "Social Cohesion Measurement" 
questions_cohesion <- c(paste("V", c(25:35, 45:48, 84:89, 108:124, 126, 141, 165:169, 212:214, 216), sep = ''))

# According to https://civicyouth.org/tools-for-practice/survey-measures-of-civic-engagement/ 
# Civic Engagement is measured mainly using politics engagement and volunteering 
questions_civic <- c(paste("V", c(226,227), sep = ""))

# Health Condition 
questions_health <- "V11"

# Working Class
questions_class <- "V238"

questions_gender <- "V240"

# Income 
questions_income_scale <- "V239"
questions_income_inequal <- "V96"

# Happiness 
questions_happy <- "V10"

# Satisfaction 
questions_satisf <- "V23"


questions_1 <- c(questions_income_scale, questions_income_inequal, questions_happy, questions_satisf)
questions_variable <- 
  wave_6_happiness %>%
  dplyr::select(V2,V2A, V11, questions_1) %>%
  filter(V11 != 4) %>%
  mutate_all(funs(replace(., .<0, NA))) %>%
  mutate(Income_Scale = 11 - V239,               # 1 is the highest group and 10 is the lowest group
         Income_Inequality = V96,                # 1 is should be more equal, 10 is should not be equal
         Happiness = V10,                        # 1 is Very Happy; 4 is Poor
         Life_Satisfaction = 11 - V23,           # 1 is very satisfied and 10 is dissatisfied
         Country = V2, Region = V2A) %>%       
  mutate(Income_Scale = as.factor(Income_Scale), 
         Income_Inequality = as.factor(Income_Inequality), 
         Happiness = as.factor(Happiness), 
         Life_Satisfaction =  as.factor(Life_Satisfaction)) %>%
  dplyr::select(Country, Region,Income_Scale, Income_Inequality, Happiness, Life_Satisfaction)
          
questions_variable <- na.omit(questions_variable)
summary(questions_variable)
```



```{r}
plots <- list()
for (i in 1:10){
  plots[[i]] <- stats_plot(i)
}
plots
```


```{r}
#m_income_scale <- polr(Happiness ~ Income_Scale, data = questions_variable, Hess=TRUE)
summary(m_income_scale)
# The AIC is 159020.81 

#m_income_inequal <- polr(Happiness ~ Income_Inequality, data = questions_variable, Hess=TRUE)
summary(m_income_inequal)
# The AIC is 160994.79  

#m_happy <- polr(Happiness ~ Income_Inequality + Income_Scale, data = questions_variable, Hess=TRUE)
summary(m_happy)
# The AIC is 158795.67 

exp(coef(m_happy))
```

```{r}
#n_income_scale <- polr(Life_Satisfaction ~ Income_Scale, data = questions_variable, Hess=TRUE)
summary(n_income_scale)
# The AIC is 320849.25 

#n_income_inequal <- polr(Life_Satisfaction ~ Income_Inequality, data = questions_variable, Hess=TRUE)
summary(n_income_inequal)
# The AIC is 324757.01 

#n_satis <- polr(Life_Satisfaction ~ Income_Inequality + Income_Scale, data = questions_variable, Hess=TRUE)
summary(n_satis)
# The AIC is 320174.42  
exp(coef(n_satis))
```


```{r}
questions_2 <- c(questions_gender, questions_income_scale,questions_happy, questions_satisf, questions_trust, questions_cohesion, questions_civic, questions_health)

question2_variable <- 
  wave_6_happiness %>%
  dplyr::select(V1,V2,V2A, questions_2) %>%
  filter(V11 != 4) %>%
  mutate_all(funs(replace(., .<0, NA))) %>%
  mutate(V45 = 4 - V45, V46 = 4 - V46, V47 = 4 - V47, V48 = 4 - V48, V141 = 11-V141) %>%
  mutate(V165 = 5-V165, V166 = 5-V166, V167 = 5-V167, V168 = 5-V168, V169 = 5-V169) %>%
  mutate(V239 = 11 - V239) %>%        # 1 is the highest group and 10 is the lowest group
  mutate(V23 = 11 - V23)              # 1 is very satisfied and 10 is dissatisfied.

US <- question2_variable %>%
  filter(V2A == 840) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)
US <- na.omit(US)
US_y_happy <- US$V10
#summary(US_y_happy)
US_x_happy <- US %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(US_x_happy) 
fit_US_happy <- glmpathcr(US_x_happy,US_y_happy)
summary(fit_US_happy)
plot(fit_US_happy, xvar = "step", type = "aic")
AIC.step_US_happy <- model.select(fit_US_happy)
AIC.step_US_happy
US_happy_coef <- nonzero.coef(fit_US_happy, s=AIC.step_US_happy)
US_happy_coef
```

So for people in the US, the significant factors for happiness:

* Income Scale

* How much you trust: Your family 

* How much you trust: People you know personally

* Active/Inactive membership: Church or religious organization

* Confidence: The police

* Confidence: The courts

* Confidence: Political Parties

* Confidence: Banks

* I see myself as part of my local community

+ Note that the glmpathcr function fits a penalized constrained continuation ratio model; therefore for K classes, there will be K-1 intercepts representing the cutpoints between adjacent classes. In this package, the nomenclature for these cutpoints is to use "cpk" where k = 1, . . . , K-1.

```{r}
US_y_satis <- US$V23
#summary(US_y_satis)
US_x_satis <- US %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(US_x_happy) 

fit_US_satis <- glmpathcr(US_x_satis,US_y_satis)
summary(fit_US_satis)

plot(fit_US_satis, xvar = "step", type = "aic")
AIC.step_US_satis <- model.select(fit_US_satis)
AIC.step_US_satis
US_satis_coef <- nonzero.coef(fit_US_satis, s=AIC.step_US_satis)
US_satis_coef
```

So for people in the US, the significant factors for Life Satisfaction:

* Income Scale

* Most people can be trusted

* How much you trust: Your family

* How much you trust: Your neighborhood

* How much you trust: People you know personally

* Active/Inactive membership: Church or religious organization

* Having a job is the best way for a woman to be an independent person.

* Political action: Joining in boycotts

* Political action: Attending peaceful demonstrations

* Confidence: The courts

* Confidence: The police

* Confidence: Political Parties

* Confidence: Banks

* Older people are a burden on society

* I see myself as a world citizen

* I see myself as part of my local community

```{r}
China <- question2_variable %>%
  filter(V2A == 156) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)
China <- sapply(China, as.numeric)
for(i in 1:ncol(China)){
  China[is.na(China[,i]), i] <- round(mean(China[,i], na.rm = TRUE))
}
China <- as.data.frame(China)
```

```{r}
China_y_happy <- China$V10
summary(China_y_happy)
China_x_happy <- China %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
summary(China_x_happy) 
fit_China_happy <- glmpathcr(China_x_happy,China_y_happy)
summary(fit_China_happy)
plot(fit_China_happy, xvar = "step", type = "aic")
AIC.step_China_happy <- model.select(fit_China_happy)
AIC.step_China_happy
China_happy_coef <- nonzero.coef(fit_China_happy, s=AIC.step_China_happy)
China_happy_coef
```

So for people in China, the significant factors for Happiness:

* Income Scale 

* Most people can be trusted

* How much you trust: Your neighborhood

* Active/Inactive membership: Political party

* If a woman earns more money than her husband, it's almost certain to cause problems

* Interest in politics

* Confidence: The police

* Confidence: Parliament

* Confidence: The Civil service

* Confidence: Environmental organizations

* How democratically is this country being governed today

* I see myself as part of the nation


```{r}
China_y_satis <- China$V23

China_x_satis <- China %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)

fit_China_satis <- glmpathcr(China_x_satis,China_y_satis)
summary(fit_China_satis)

plot(fit_China_satis, xvar = "step", type = "aic")
AIC.step_China_satis <- model.select(fit_China_satis)
AIC.step_China_satis
China_satis_coef <- nonzero.coef(fit_China_satis, s=AIC.step_China_satis)
China_satis_coef
```

So for people in China, the significant factors for Life Satisfaction:

* Scale of Income 

* Active/Inactive membership: Political party

* If a woman earns more money than her husband, it's almost certain to cause problems

* Interest in politics

* Confidence: The police

* Confidence: Parliament

* Confidence: The Civil service

* Confidence: Universities

* Confidence: Banks

* Confidence: Major Companies

* How democratically is this country being governed today

* Old people have too much political influence

* I see myself as part of the nation

```{r}
Female <- question2_variable %>%
  filter(V240 == 2) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)

Female <- na.omit(Female)
Female_y_happy <- Female$V10
#summary(Female_y_happy)
Female_x_happy <- Female %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(Female_x_happy) 
fit_Female_happy <- glmpathcr(Female_x_happy,Female_y_happy)
summary(fit_Female_happy)
plot(fit_Female_happy, xvar = "step", type = "aic")
AIC.step_Female_happy <- model.select(fit_Female_happy)
AIC.step_Female_happy
Female_happy_coef <- nonzero.coef(fit_Female_happy, s=AIC.step_Female_happy)
Female_happy_coef
```

Significant Factors for Female Interviewees' Happiness: 

* Income Scale

* How much you trust: Your family

* How much you trust: People of another religion

* How much you trust: People of another nationality

* Active/Inactive membership: Church or religious organization

* Active/Inactive membership: Art, music or educational organization

* Active/Inactive membership: Environmental organization

* Active/Inactive membership: Humanitarian or charitable organization

* Having a job is the best way for a woman to be an independent person

* Interest in politics

* Political action: Signing a petition

* Political action: Joining in boycotts

* Political action: Any other act of protest

* Confidence: The Churches

* Confidence: Labour Unions

* Confidence: The government (in your nation's capital)

* Confidence: The Civil service

* Confidence: Universities

* Confidence: Environmental organizations

* Confidence: Women's organizations

* How democratically is this country being governed today

* Older people get more than their fair share from the government

* Older people are a burden on society

* Old people have too much political influence

* I see myself as a world citizen

* I see myself as part of my local community

* I see myself as part of the nation

* I see myself as an autonomous individual


```{r}
Male <- question2_variable %>%
  filter(V240 == 1) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)
Male <- na.omit(Male)
Male_y_happy <- Male$V10
#summary(Female_y_happy)
Male_x_happy <- Male %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(Female_x_happy) 
fit_Male_happy <- glmpathcr(Male_x_happy,Male_y_happy)
summary(fit_Male_happy)
plot(fit_Male_happy, xvar = "step", type = "aic")
AIC.step_Male_happy <- model.select(fit_Male_happy)
AIC.step_Male_happy
Male_happy_coef <- nonzero.coef(fit_Male_happy, s=AIC.step_Male_happy)
Male_happy_coef
```

Significant Factors for Male Interviewees' Happiness: 

* Income Scale 

* How much you trust: Your family

* How much you trust: Your neighborhood

* How much you trust: People of another nationality

* Active/Inactive membership: Church or religious organization

* Active/Inactive membership: Sport or recreational organization

* Active/Inactive membership: Humanitarian or charitable organization

* When jobs are scarce, employers should give priority to people of this country over immigrants.

* Political action: Joining in boycotts

* Political action: Attending peaceful demonstrations

* Political action: Any other act of protest

* Confidence: The Churches

* Confidence: The armed forces

* Confidence: The government (in your nation's capital)

* Confidence: Parliament

* Confidence: Universities

* Confidence: Major Companies

* Confidence: Banks

* How democratically is this country being governed today

* Older people get more than their fair share from the government

* Old people have too much political influence

* I see myself as a world citizen

* I see myself as part of the nation

* I see myself as an autonomous individual



```{r}
Scale_higher <- question2_variable %>%
  filter(V239 == 1 | V239 == 2 | V239 == 3) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240, -V239)
Scale_higher <- na.omit(Scale_higher)
Scale_higher_y_happy <- Scale_higher$V10
#summary(Female_y_happy)
Scale_higher_x_happy <- Scale_higher %>%
  dplyr::select(questions_trust, questions_cohesion, questions_civic)
#summary(Female_x_happy) 
fit_Scale_higher_happy <- glmpathcr(Scale_higher_x_happy,Scale_higher_y_happy)
summary(fit_Scale_higher_happy)
plot(fit_Scale_higher_happy, xvar = "step", type = "aic")
AIC.step_Scale_higher_happy <- model.select(fit_Scale_higher_happy)
AIC.step_Scale_higher_happy
Scale_higher_happy_coef <- nonzero.coef(fit_Scale_higher_happy, s=AIC.step_Scale_higher_happy)
Scale_higher_happy_coef

```
   V102          V25         V108         V111         V114         V120         V121         V123         V212         V214 
0.020265166 -0.071288906  0.078352030  0.023665955  0.030836338  0.003678585  0.016129620  0.029791060  0.220894937  0.059535522 
   V216       
 0.025730851  

* How much you trust: Your family

* Active/Inactive membership: Church or religious organization

* Confidence: The Churches

* Confidence: Television

* Confidence: The courts

* Confidence: Major Companies

* Confidence: Banks

* Confidence: Women's organizations

* I see myself as a world citizen

* I see myself as part of the nation

* I see myself as an autonomous individual

```{r}
Scale_lower <- question2_variable %>%
  filter(V239 == 8 | V239 == 9 | V239 == 10) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240, -V239)
Scale_lower <- na.omit(Scale_lower)
Scale_lower_y_happy <- Scale_lower$V10
#summary(Female_y_happy)
Scale_lower_x_happy <- Scale_lower %>%
  dplyr::select(questions_trust, questions_cohesion, questions_civic)
#summary(Female_x_happy) 
fit_Scale_lower_happy <- glmpathcr(Scale_lower_x_happy,Scale_lower_y_happy)
summary(fit_Scale_lower_happy)
plot(fit_Scale_lower_happy, xvar = "step", type = "aic")
AIC.step_Scale_lower_happy <- model.select(fit_Scale_lower_happy)
AIC.step_Scale_lower_happy
Scale_lower_happy_coef <- nonzero.coef(fit_Scale_lower_happy, s=AIC.step_Scale_lower_happy)
Scale_lower_happy_coef

```
   V102         V107         V25           V26          V32          V45          V46          V86          V88         V112 
0.077727946 -0.008422508 -0.123113586 -0.091790250 -0.073952218  0.023139076  0.055546347 -0.099898658 -0.013064716 -0.009474266  

    V115         V118         V119         V121         V123         V141         V166         V167         V212         V213         V216 
 0.010785299 -0.060599942  0.012759995  0.036998026  0.037502582  0.051210555 -0.021273624  0.034494060  0.135460655  0.012525385  0.025042014


* How much you trust: Your family

* How much you trust: People of another nationality

* Active/Inactive membership: Church or religious organization

* Active/Inactive membership: Sport or recreational organization

* Active/Inactive membership: Humanitarian or charitable organization

* When jobs are scarce, men should have more right to a job than women

* When jobs are scarce, employers should give priority to people of this country over immigrants

* Political action: Joining in boycotts

* Political action: Joining strikes

* Confidence: Labour Unions

* Confidence: The government (in your nation's capital)

* Confidence: The Civil service

* Confidence: Universities

* Confidence: Women's organizations

* How democratically is this country being governed today

* Older people get more than their fair share from the government

* Older people are a burden on society

* I see myself as a world citizen

* I see myself as part of my local community

* I see myself as an autonomous individual



