---
title: "Happiness Report"
author: "Zhu Shen"
date: "November 6, 2018"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(MASS)
library(reshape2)
library(ggthemes)
library(stargazer)
library(glmpathcr)
```

## R Markdown
```{r, include = FALSE}
wave_6_happiness <- readRDS("F00007762-WV6_Data_R_v20180912.rds", refhook = NULL)
```

## Brief Speculation fo the dataset

```{r}
# Find the keyword TRUST
questions_trust <- c(paste("V", c(24, 102:107), sep = ''))
#confounding_trust <- "V160B" 

# According to Paper "Social Cohesion Measurement" 
questions_cohesion <- c(paste("V", c(25:35, 45:48, 84:89, 108:124, 126, 141, 165:169, 212:214, 216), sep = ''))

# According to https://civicyouth.org/tools-for-practice/survey-measures-of-civic-engagement/ 
# Civic Engagement is measured mainly using politics engagement and volunteering 
questions_civic <- c(paste("V", c(226,227), sep = ""))

# Health Condition 
questions_health <- "V11"

# Working Class
questions_class <- "V238"

questions_gender <- "V240"

# Income 
questions_income_scale <- "V239"
questions_income_inequal <- "V96"

# Happiness 
questions_happy <- "V10"

# Satisfaction 
questions_satisf <- "V23"


questions_1 <- c(questions_income_scale, questions_income_inequal, questions_happy, questions_satisf)
questions_variable <- 
  wave_6_happiness %>%
  dplyr::select(V2,V2A, V11, questions_1) %>%
  filter(V11 != 4) %>%
  mutate_all(funs(replace(., .<0, NA))) %>%
  mutate(Income_Scale = 11 - V239,               # 1 is the highest group and 10 is the lowest group
         Income_Inequality = V96,                # 1 is should be more equal, 10 is should not be equal
         Happiness = V10,                        # 1 is Very Happy; 4 is Poor
         Life_Satisfaction = 11 - V23,           # 1 is very satisfied and 10 is dissatisfied
         Country = V2, Region = V2A) %>%       
  mutate(Income_Scale = as.factor(Income_Scale), 
         Income_Inequality = as.factor(Income_Inequality), 
         Happiness = as.factor(Happiness), 
         Life_Satisfaction =  as.factor(Life_Satisfaction)) %>%
  dplyr::select(Country, Region,Income_Scale, Income_Inequality, Happiness, Life_Satisfaction)
          
questions_variable <- na.omit(questions_variable)
summary(questions_variable)
```



```{r}
summary(as.numeric(questions_variable$Income_Scale))
by_income_scale_1 <- questions_variable %>%
  filter(Income_Scale == 1) %>%
  group_by(Income_Inequality) %>%
  summarize(count = n(), 
            prop = count/1166)

p1 <- ggplot(by_income_scale_1,aes(x=Income_Inequality,y=prop, width=.6))+
  geom_bar(stat="identity")+
  scale_x_discrete(name ="Level", 
                   breaks=seq(0,10,1)) + 
  ylab("Prop") +
  theme_bw()
p1



by_income_scale_5 <- questions_variable %>%
  filter(Income_Scale == 5) %>%
  group_by(Income_Inequality) %>%
  summarize(count = n(), 
            prop = count/12493)

p5 <- ggplot(by_income_scale_5,aes(x=Income_Inequality,y=prop, width=.6))+
  geom_bar(stat="identity")+
  scale_x_discrete(name ="Level", 
                   breaks=seq(0,10,1)) + 
  ylab("Prop") +
  theme_bw()
p5



by_income_scale_10 <- questions_variable %>%
  filter(Income_Scale == 10) %>%
  group_by(Income_Inequality) %>%
  summarize(count = n(), 
            prop = count/5692)

p10 <- ggplot(by_income_scale_10,aes(x=Income_Inequality,y=prop, width=.6))+
  geom_bar(stat="identity")+
  scale_x_discrete(name ="Level", 
                   breaks=seq(0,10,1)) + 
  ylab("Prop") +
  theme_bw()
p10

```


```{r}
p <- ggplot(by_income_scale,aes(x=Income_Scale,y=unequal_prop, width=.6))+
  geom_bar(stat="identity")+
  scale_x_discrete(name ="Level", 
                   breaks=seq(0,10,1)) + 
  ylab("Mean") +
  theme_bw()
p

Income_Inequality <- summary(questions_variable$Income_Inequality)
df <- as.data.frame(cbind(Income_Scale, Income_Inequality)) %>%
  mutate(level = 1:10)
df<-melt(df,id.vars="level")

p1 <- ggplot(df,aes(x=level,y=value,fill=factor(variable), width=.6))+
  geom_bar(stat="identity",position="dodge")+
  scale_x_continuous(name ="Level", 
                   breaks=seq(0,10,1)) + 
  ylab("Number of Response") +
  theme_bw()+ 
  scale_fill_manual(name = "Income or Perception of Inequality", 
                      values=c("#E69F00","#56B4E9")) + 
  labs(title = "Comparison of People's Income and Perceptions of Income Inequality", 
       subtitle = 
         "Level 1: Highest Income Scale / Income should be made more equal\nLevel 10: Lowest Income Scale / Larger income differences as incentives",
       caption = "Source: World Value Survey")
p1
```
??????make sense
??????level of income?????????


```{r}
#m_income_scale <- polr(Happiness ~ Income_Scale, data = questions_variable, Hess=TRUE)
summary(m_income_scale)
# The AIC is 159020.81 

#m_income_inequal <- polr(Happiness ~ Income_Inequality, data = questions_variable, Hess=TRUE)
summary(m_income_inequal)
# The AIC is 160994.79  

#m_happy <- polr(Happiness ~ Income_Inequality + Income_Scale, data = questions_variable, Hess=TRUE)
summary(m_happy)
# The AIC is 158795.67 

exp(coef(m_happy))
```

```{r}
#n_income_scale <- polr(Life_Satisfaction ~ Income_Scale, data = questions_variable, Hess=TRUE)
summary(n_income_scale)
# The AIC is 320849.25 

#n_income_inequal <- polr(Life_Satisfaction ~ Income_Inequality, data = questions_variable, Hess=TRUE)
summary(n_income_inequal)
# The AIC is 324757.01 

#n_satis <- polr(Life_Satisfaction ~ Income_Inequality + Income_Scale, data = questions_variable, Hess=TRUE)
summary(n_satis)
# The AIC is 320174.42  
exp(coef(n_satis))
```


```{r}
questions_2 <- c(questions_gender, questions_income_scale,questions_happy, questions_satisf, questions_trust, questions_cohesion, questions_civic, questions_health)

question2_variable <- 
  wave_6_happiness %>%
  dplyr::select(V1,V2,V2A, questions_2) %>%
  filter(V11 != 4) %>%
  mutate_all(funs(replace(., .<0, NA))) %>%
  mutate(V45 = 4 - V45, V46 = 4 - V46, V47 = 4 - V47, V48 = 4 - V48, V141 = 11-V141) %>%
  mutate(V165 = 5-V165, V166 = 5-V166, V167 = 5-V167, V168 = 5-V168, V169 = 5-V169) %>%
  mutate(V239 = 11 - V239) %>%        # 1 is the highest group and 10 is the lowest group
  mutate(V23 = 11 - V23)              # 1 is very satisfied and 10 is dissatisfied.

US <- question2_variable %>%
  filter(V2A == 840) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)
US <- na.omit(US)
US_y_happy <- US$V10
#summary(US_y_happy)
US_x_happy <- US %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(US_x_happy) 
fit_US_happy <- glmpathcr(US_x_happy,US_y_happy)
summary(fit_US_happy)
plot(fit_US_happy, xvar = "step", type = "aic")
AIC.step_US_happy <- model.select(fit_US_happy)
AIC.step_US_happy
US_happy_coef <- nonzero.coef(fit_US_happy, s=AIC.step_US_happy)
US_happy_coef
```
So for people in the US, the significant factors for happiness:

* Income Scale

* How much you trust: Your family 

* How much you trust: People you know personally

* Active/Inactive membership: Church or religious organization

* Confidence: The police

* Confidence: The courts

* Confidence: Political Parties

* Confidence: Banks

* I see myself as part of my local community

+ Note that the glmpathcr function fits a penalized constrained continuation ratio model; therefore for K classes, there will be K-1 intercepts representing the cutpoints between adjacent classes. In this package, the nomenclature for these cutpoints is to use "cpk" where k = 1, . . . , K-1.

```{r}
US_y_satis <- US$V23
#summary(US_y_satis)
US_x_satis <- US %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(US_x_happy) 

fit_US_satis <- glmpathcr(US_x_satis,US_y_satis)
summary(fit_US_satis)

plot(fit_US_satis, xvar = "step", type = "aic")
AIC.step_US_satis <- model.select(fit_US_satis)
AIC.step_US_satis
US_satis_coef <- nonzero.coef(fit_US_satis, s=AIC.step_US_satis)
US_satis_coef
```

So for people in the US, the significant factors for Life Satisfaction:

* Income Scale

* Most people can be trusted

* How much you trust: Your family

* How much you trust: Your neighborhood

* How much you trust: People you know personally

* Active/Inactive membership: Church or religious organization

* Having a job is the best way for a woman to be an independent person.

* Political action: Joining in boycotts

* Political action: Attending peaceful demonstrations

* Confidence: The courts

* Confidence: The police

* Confidence: Political Parties

* Confidence: Banks

* Older people are a burden on society

* I see myself as a world citizen

* I see myself as part of my local community

```{r}
China <- question2_variable %>%
  filter(V2A == 156) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)
China <- na.omit(China)
China_y_happy <- China$V10
summary(China_y_happy)
China_x_happy <- China %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
summary(China_x_happy) 
fit_China_happy <- glmpathcr(China_x_happy,China_y_happy)
summary(fit_China_happy)
plot(fit_China_happy, xvar = "step", type = "aic")
AIC.step_China_happy <- model.select(fit_China_happy)
AIC.step_China_happy
China_happy_coef <- nonzero.coef(fit_China_happy, s=AIC.step_China_happy)
China_happy_coef
```



```{r}
Female <- question2_variable %>%
  filter(V240 == 2) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)

Female <- na.omit(Female)
Female_y_happy <- Female$V10
#summary(Female_y_happy)
Female_x_happy <- Female %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(Female_x_happy) 
fit_Female_happy <- glmpathcr(Female_x_happy,Female_y_happy)
summary(fit_Female_happy)
plot(fit_Female_happy, xvar = "step", type = "aic")
AIC.step_Female_happy <- model.select(fit_Female_happy)
AIC.step_Female_happy
Female_happy_coef <- nonzero.coef(fit_Female_happy, s=AIC.step_Female_happy)
Female_happy_coef
```
Significant Factors for Female Interviewees' Happiness: 

* Income Scale

* How much you trust: Your family

* How much you trust: People of another religion

* How much you trust: People of another nationality

* Active/Inactive membership: Church or religious organization

* Active/Inactive membership: Sport or recreational organization

* Active/Inactive membership: Art, music or educational organization

* Active/Inactive membership: Environmental organization

* Active/Inactive membership: Humanitarian or charitable organization

* Having a job is the best way for a woman to be an independent person

* Interest in politics

* Political action: Signing a petition

* Political action: Joining in boycotts

* Political action: Any other act of protest

* Confidence: The Churches

* Confidence: Labour Unions

* Confidence: The government (in your nation's capital)

* Confidence: The Civil service

* Confidence: Universities

* Confidence: Banks

* Confidence: Environmental organizations

* Confidence: Women's organizations

* How democratically is this country being governed today

* Older people get more than their fair share from the government

* Older people are a burden on society

* Old people have too much political influence

* I see myself as a world citizen

* I see myself as part of my local community

* I see myself as part of the nation

* I see myself as an autonomous individual


```{r}
Male <- question2_variable %>%
  filter(V240 == 1) %>%
  dplyr::select(-V1, -V2, -V2A, -V11, -V240)
Male <- na.omit(Male)
Male_y_happy <- Male$V10
#summary(Female_y_happy)
Male_x_happy <- Male %>%
  dplyr::select(V239, questions_trust, questions_cohesion, questions_civic)
#summary(Female_x_happy) 
fit_Male_happy <- glmpathcr(Male_x_happy,Male_y_happy)
summary(fit_Male_happy)
plot(fit_Male_happy, xvar = "step", type = "aic")
AIC.step_Male_happy <- model.select(fit_Male_happy)
AIC.step_Male_happy
Male_happy_coef <- nonzero.coef(fit_Male_happy, s=AIC.step_Male_happy)
Male_happy_coef
```
V239          V102          V103          V107           V25           V26           V32           V45           V46 
V47           V86           V87           V89          V108          V109          V115          V117          V119          V120 
 V121          V123          V141          V166          V169          V212          V214          V216



```



```{r}
US_China <- wave_6_happiness_variable %>%
  dplyr::select(-Region) %>%
  #mutate(Trust = as.factor(round(Trust)), 
       #  Cohesion = as.factor(round(Cohesion)), 
      #   Civic = as.factor(Civic)) %>%
  filter((Country == 840) | (Country == 156)) %>%
  mutate(Country = as.factor(ifelse(Country == 840, "US", "China")))

str(US_China)

colors <- c("#999999", "#E69F00")
colors <- colors[as.numeric(US_China$Country)]

p_trust_satisfaction <- ggplot(data = US_China, aes(x = Trust, y = Happiness, col = Country)) + 
  geom_point(pch = 16, alpha = 0.8, size = 2)
p_trust_satisfaction

```



```{r}
#om3 <- clm(Happiness ~ Income_Class * Health, data = wave_6_happiness_variable)
#summary(om3)

#om4 <- clm(Life_Satisfaction ~ Income_Class * Health, data = wave_6_happiness_variable)
#summary(om4)


lm1 <- lm(Trust~Income_Scale, data=US)
summary(lm1)

lm2 <- lm(Cohesion~Income_Scale, data = US)
summary(lm2)

lm3 <- lm(Civic~Income_Scale, data = US)
summary(lm3)

lm4 <- clm(Life_Satisfaction ~ Civic, data = US)
summary(lm4)

lm5 <- clm(Life_Satisfaction ~ Trust*Income_Scale, data = US)
summary(lm5)

HIGH_1 <- wave_6_happiness_variable %>%
  filter(Income_Class == 1)
summary(HIGH_1)
cm6 <- clm(Happiness ~ Trust+Cohesion+Civic, data = HIGH_1)
summary(cm6)
# The highest income group is a highest social connected group

HIGH_2 <- wave_6_happiness_variable %>%
  filter(Income_Class == 2)
summary(HIGH_2)
cm7 <- clm(Happiness ~ Trust+Cohesion+Civic, data = HIGH_2)
summary(cm7)
# The second highest income group is intertrusted group, social connected group and civic engaged group

HIGH_3 <- wave_6_happiness_variable %>%
  filter(Income_Class == 3)
summary(HIGH_3)
cm8 <- clm(Happiness ~ Trust+Cohesion+Civic, data = HIGH_3)
summary(cm8)
# The third highest income group is social connected and civic engaged group

HIGH_4 <- wave_6_happiness_variable %>%
  filter(Income_Class == 4)
summary(HIGH_4)
cm9 <- clm(Happiness ~ Trust+Cohesion+Civic, data = HIGH_4)
summary(cm9)
# Very social connected but less civic engaged than group 2 and group 3

HIGH_5 <- wave_6_happiness_variable %>%
  filter(Income_Class == 5)
summary(HIGH_5)
cm10 <- clm(Happiness ~ Trust+Cohesion+Civic, data = HIGH_5)
summary(cm10)
# Surprisingly, it is a highly intertrusted group and highly social connected group
```







